---
output:
  html_document: default
  pdf_document: default
---
# Red Wine Quality Analysis

* by Roger Duong
* V2
* May 2018

========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
library(ggplot2)
library(gridExtra)
library(dplyr)
library(GGally)
library(RColorBrewer)
library(colorspace)
library(MASS)
library(memisc)
library(ROCR)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
wine <- read.csv('wineQualityReds.csv')
```

This report explores a dataset containing quality ratings and 11 chemical
properties for approximately 1,600 wines. Below is a summary of the dataset.
We have transformed the label 'quality' into an ordered factor, to facilitate
later plotting.

```{r echo=FALSE}
str(wine)
```

```{r echo=FALSE}
head(wine)
```

```{r}
summary(wine)
```

```{r echo=FALSE}
wine$quality <- ordered(wine$quality, levels = c(3, 4, 5, 6, 7, 8))
wine$other.sulfur.dioxide <- wine$total.sulfur.dioxide - 
  wine$free.sulfur.dioxide
wine <- wine[c(1, 2, 3, 4, 5, 6, 7, 14, 8, 9, 10, 11, 12, 13)]
```

# Univariate Plots Section

The following section displays 10 univariate plots, which will help to 
understand the structure of the individual variables in the wine dataset.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_1}
ggplot(data = wine, aes(x = quality)) +
  geom_histogram(stat = 'count')
```

We observe that the majority of wines are rated 5 and 6 with a maximum
rating of 8. The purpose of this analysis is to identify which chemical
properties (features) influence the quality of wines (label).

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_2}
ggplot(data = wine, aes(x = fixed.acidity)) +
  geom_histogram(binwidth = 0.2)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_3}
ggplot(data = wine, aes(x = residual.sugar)) +
  geom_histogram(binwidth = 0.2)
```

The distribution of residual sugar shows multiple outliers, with values above 8.
The mode appears to be around the region of 2.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_4}
ggplot(data = wine[wine$residual.sugar < 3,], aes(x = residual.sugar)) +
  geom_histogram(binwidth = 0.1)
```

I have limited the observations of residual sugar to a shorter interval to
better see what was happening around the peak of count observed around 2.0.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_5}
ggplot(data = wine, aes(x = chlorides)) +
  geom_histogram(binwidth = 0.01)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_6}
ggplot(data = wine[wine$chlorides < 0.15,], aes(x = chlorides)) +
  geom_histogram(binwidth = 0.005)
```

Likewise for chorides, we can observe a long-tailed distribution, with a mode
at 0.08.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_7}
ggplot(data = wine, aes(x = total.sulfur.dioxide)) +
  geom_histogram()
```

We can observe that the total sulfur dioxide distribution is positively skewed

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_8}
ggplot(data = wine, aes(x = pH)) +
  geom_histogram()
```

We can observe that the mode is in the region of 3.3, which is an acid solution.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_9}
ggplot(data = wine, aes(x = sulphates)) +
  geom_histogram()
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots_10}
ggplot(data = wine[wine$sulphates < 1,], aes(x = sulphates)) +
  geom_histogram(binwidth = 0.01)
```

We can observe that the sulphate distribution is positively skewed, with a mode
around 0.6.

# Univariate Analysis

**What is the structure of your dataset?**

There are 1,600 wines in the dataset, with 11 features: fixed acidity,
volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide,
total sulfur dioxide, density,  pH, sulphates, and alcohol.
The variable X is just an index number and will not be used for this analysis.

All variables are numerical.

Some observations:

* Most wines are rated 5 or 6
* Wines are acid, with pH mean at 3.3
* Alcohol contents of wines are on average at 10 %

**What is/are the main feature(s) of interest in your dataset?**

The main features are the acidic properties of the wines (pH, fixed acidity,
volatile acidity, citric acid) and alcohol properties of the wines. We will
examine how those features can predict the label of wine quality.

**What other features in the dataset do you think will help support your**
**investigation into your feature(s) of interest?**

Other features like sugar, sulfur will help examine the relationship between
chemical properties and wine quality.

**Did you create any new variables from existing variables in the dataset?**

I did create the new variable 'other.sulfur.dioxide' being the difference
between the total sulfur dioxide and the free sulfur dioxide.

**Of the features you investigated, were there any unusual distributions?**
**Did you perform any operations on the data to tidy, adjust, or change the**
**form of the data? If so, why did you do this?**

I converted the label 'quality' from a numerical type to an ordered factor.

# Bivariate Plots Section

This section describes the relationships between 2 variables. It starts by
plotting a pair plot, which will help to visualize correlations between
variables.

```{r echo=FALSE, message=FALSE, warning=FALSE, Pair_Plots}
ggcorr(subset(wine, select = -X))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Correlation_Matrix}
ggcorr(subset(wine, select = -X), geom = "blank", label = TRUE, hjust = 0.75) +
  geom_point(size = 10, aes(color = coefficient > 0,
                            alpha = abs(coefficient) > 0.5)) +
  scale_alpha_manual(values = c("TRUE" = 0.25, "FALSE" = 0)) +
  guides(color = FALSE, alpha = FALSE)
```

Using the visualization from the pair plot, I propose to investigate further
the correlation between:

* quality and volatile acidity
* quality and citric acid
* quality and sulphates
* quality and alcohol

Selecting the largest correlation coefficient from the correlation matrix,
I propose to study in more details the following correlations between:

* fixed acidity and citric acid
* volatile acidity and citric acid
* fixed acidity and pH
* citric acid and pH
* free sulfur dioxide and total sulfur dioxide
* fixed acidity and density
* density and alcohol

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_1}
ggplot(data = wine, aes(x = quality, y = volatile.acidity)) +
  geom_boxplot()
```

We can observe that the interquartile ranges vary from between wines of 
different quality. This should be explored further with an ordinal logistic
regression later.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_2}
ggplot(data = wine, aes(x = quality, y = citric.acid)) +
  geom_boxplot()
```

We can also observe that the citric acid level vary from wines of poor quality
to wines of high quality. We will investigate further later.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_3}
ggplot(data = wine, aes(x = quality, y = sulphates)) +
  geom_boxplot()
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_4}
ggplot(data = wine, aes(x = quality, y = alcohol)) +
  geom_boxplot()
```

We can observe that high quality wines (7 and 8) have higher alcohol content
generally above 11%.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_5}
ggplot(data = wine, aes(x = citric.acid, y = fixed.acidity)) +
  xlim(c(0, 0.75)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_5}
mb5 <- lm(fixed.acidity ~ citric.acid, data = wine)
```

We can observe a moderate correlation between fixed acidity and citric acid, 
with a R^2 value of `r round(summary(mb5)$r.squared, 3)`.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_6}
ggplot(data = wine, aes(x = citric.acid, y = volatile.acidity)) +
  xlim(c(0, 0.75)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_6}
mb6 <- lm(volatile.acidity ~ citric.acid, data = wine)
```

We can observe a moderate correlation between volatile acidity and citric acid,
with a R^2 value of `r round(summary(mb6)$r.squared, 3)`

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9}
ggplot(data = wine, aes(x = fixed.acidity, y = pH)) +
  scale_x_log10() +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_9}
mb9_1_1 <- lm(pH ~ fixed.acidity, data = wine)
mb9_1_2 <- lm(pH ~ log(fixed.acidity), data = wine)
```

We can observe a moderate correlation between the log of fixed acidity and pH,
with a R^2 value of `r round(summary(mb9_1_2)$r.squared, 3)`.

We can observe a lot of dispersion, around a general trendline. Let's smooth
the data by calculating the mean pH for values of fixed acidity.

```{r echo=FALSE, message=FALSE, warning=FALSE, Smoothing_9_4}
wine_fixed_pH <- wine %>%
  group_by(fixed.acidity) %>%
  summarise(pH.mean = mean(pH),
            pH.median = median(pH),
            n = n())
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9_4}
ggplot(data = wine_fixed_pH, aes(x = fixed.acidity, y = pH.mean)) +
  scale_x_log10() +
  geom_point() +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_9_4}
mb9_4 <- lm(pH.mean ~ log(fixed.acidity), data = wine_fixed_pH)
```

We can observe a good correlation between log fixed acidity and pH mean, with 
a R^2 value of `r round(summary(mb9_4)$r.squared, 3)`. 

This is expected as the pH is a function of the log concentration of H+ ions,
which is proportional to the fixed acidity concentration.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9_2}
ggplot(data = wine, aes(x = citric.acid, y = pH)) +
  xlim(c(0, 0.75)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_9_2}
mb9_2_1 <- lm(pH ~ citric.acid, data = wine)
```

We can observe a weak correlation between citric acid and pH, with 
a R^2 value of `r round(summary(mb9_2_1)$r.squared, 3)`.

We can observe a lot of dispersion, around a general trendline. Let's smooth
the data by calculating the mean pH for values of citric acid.

```{r echo=FALSE, message=FALSE, warning=FALSE, Smoothing_9_3}
wine_citric_pH <- wine %>%
  group_by(citric.acid) %>%
  summarise(pH.mean = mean(pH),
            pH.median = median(pH),
            n = n())
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_9_3}
ggplot(data = wine_citric_pH, aes(x = citric.acid, y = pH.mean)) +
  xlim(c(0, 0.75)) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_9_3}
mb9_3 <- lm(pH.mean ~ citric.acid, data = wine_citric_pH)
```

We can observe a good correlation between citric acid and pH mean, with 
a R^2 value of `r round(summary(mb9_3)$r.squared, 3)`.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_7}
ggplot(data = wine, aes(x = free.sulfur.dioxide, y = total.sulfur.dioxide)) +
  geom_jitter(alpha = 0.25, size = 1) +
  geom_smooth(method = lm, formula = y~0+x)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_7}
mb7 <- lm(total.sulfur.dioxide ~ 0 + free.sulfur.dioxide, data = wine)
```

We can observe a good correlation between total sulfur dioxide and free
sulfur dioxide, with a R^2 value of `r round(summary(mb7)$r.squared, 3)`.

This is expected as the two variables are colinear.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_8}
ggplot(data = wine, aes(x = density, y = fixed.acidity)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_8}
mb8 <- lm(fixed.acidity ~ density, data = wine)
```

We can observe moderate correlation between fixed acidity and density, with
a R^2 value of `r round(summary(mb8)$r.squared, 3)`.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots_10}
ggplot(data = wine, aes(x = alcohol, y = density)) +
  geom_jitter(alpha = 0.25) +
  geom_smooth(method = lm)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, Model_Biv_10}
mb10 <- lm(density ~ alcohol, data = wine)
```

We can observe weak correlation between density and alcohol, with
a R^2 value of `r round(summary(mb10)$r.squared, 3)`.

# Bivariate Analysis

**Talk about some of the relationships you observed in this part of the**
**investigation. How did the feature(s) of interest vary with other features**
**in the dataset?**

Using the visualization from the pair plot, we can observe good correlation
between:

* quality and volatile acidity
* quality and citric acid
* quality and sulphates
* quality and alcohol

**Did you observe any interesting relationships between the other features**
**(not the main feature(s) of interest)?**

The scatter plots and simple linear models allowed us to observe good
correlation between the following features:

* free sulfur dioxide and total sulfur dioxide
* citric acid and pH mean
* fixed acidity and pH mean

Those correlations above are expected because the chemical properties are
chemically dependent between each other.

The scatter plots and simple linear models allowed us to observe moderate
correlation between the following features:

* fixed acidity and citric acid
* volatile acidity and citric acid
* fixed acidity and pH
* fixed acidity and density

The scatter plots and simple linear models allowed us to observe weak
correlation between the following features:

* citric acid and pH
* density and alcohol

As such, if we were to use them in a prediction model, we should be cautious
about mistakenly showing spurious correlations.

**What was the strongest relationship you found?**

The strongest relationship for the quality of wine was found with the volatile
acidity.

# Multivariate Plots Section

In this section, we choose to plot scatterpolts between features that have shown
strong relationships previously and add a third variable being the main label
of interest (quality).

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_1}
ggplot(data = wine, aes(x = citric.acid, y = volatile.acidity,
                        color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  geom_smooth(method = lm, se = FALSE) +
  scale_color_brewer(palette = 'RdYlGn')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_2}
ggplot(data = wine, aes(x = citric.acid, y = fixed.acidity, color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  geom_smooth(method = lm, se = FALSE) +
  scale_color_brewer(palette = 'RdYlGn')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_3}
ggplot(data = wine, aes(x = density, y = fixed.acidity, color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  geom_smooth(method = lm, se = FALSE) +
  scale_color_brewer(palette = 'RdYlGn')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_4}
ggplot(data = wine, aes(x = alcohol, y = density, color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  geom_smooth(method = lm, se = FALSE) +
  scale_color_brewer(palette = 'RdYlGn')
```

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots_5}
ggplot(data = wine, aes(x = alcohol, y = volatile.acidity, color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  scale_color_brewer(palette = 'RdYlGn')
```

We can observe on the previous lots that wines of good quality (7 and 8, in
green) are generally clustered separately from wines of low quality (3 and 4,
in red and orange).

# Multivariate Analysis

**Talk about some of the relationships you observed in this part of the**
**investigation. Were there features that strengthened each other in terms of**
**looking at your feature(s) of interest?**

The relationship between the label quality and volatile acidity, alcohol were
strengthened.

**Were there any interesting or surprising interactions between features?**

The relationship between density on fixed acidity showed interaction.

**OPTIONAL: Did you create any models with your dataset? Discuss the**
**strengths and limitations of your model.**

We created an ordinal logistic regression model using the MASS library. The
purpose of the model is to predict the wine quality using the features available
in the dataset.

The relationship studied was:

quality ~ volatile.acidity + alcohol + fixed.acidity + density +
  citric.acid + sulphates

We splitted the dataset into test and training sets. We then created several
models by adding features one by one, in order to study the influence of those
features in our ability to predict the wine quality. The metric used to evaluate
the performance of the model was the accuracy.

We included a model that uses all features as variables to our model.

```{r}
#Splitting test and train sets
set.seed(1000)
wine_train <- sample_frac(wine, 0.75)
wine_test <- sample_frac(wine, 0.25)

# Models adding one variable at the time

m1 <- polr(quality ~ volatile.acidity, data = wine_train)
m2 <- update(m1, ~ . + alcohol)
m3 <- update(m2, ~ . + density)
m4 <- update(m3, ~ . + fixed.acidity)
m5 <- update(m4, ~ . + sulphates)
m6 <- update(m5, ~ . + citric.acid)

# Model with all variables
m7 <- polr(quality ~ volatile.acidity + alcohol + density + fixed.acidity +
             sulphates + citric.acid + residual.sugar + chlorides +
             free.sulfur.dioxide + other.sulfur.dioxide + pH,
           data = wine_train)
summary(m7)
```

```{r}
results <- data.frame(wine_test$quality)
colnames(results)[1] <- 'actual'

results$predicted.1 <- ordered(predict(m1, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.2 <- ordered(predict(m2, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.3 <- ordered(predict(m3, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.4 <- ordered(predict(m4, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.5 <- ordered(predict(m5, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.6 <- ordered(predict(m6, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))
results$predicted.7 <- ordered(predict(m7, newdata = wine_test),
                               levels = c(3, 4, 5, 6, 7, 8))

```

The following shows the actual quality and the quality rating predicted by the 6
models we created.

```{r}
head(results)
```

The following shows the accuracy score for each of the 6 models we created.

```{r}
misClasificError <- c(mean(results$predicted.1 != results$actual),
                      mean(results$predicted.2 != results$actual),
                      mean(results$predicted.3 != results$actual),
                      mean(results$predicted.4 != results$actual),
                      mean(results$predicted.5 != results$actual),
                      mean(results$predicted.6 != results$actual),
                      mean(results$predicted.7 != results$actual))
print(1-misClasificError)
```

We can observe that the performance of the model is pretty weak, with accuracy
scores barely above 0.5, which means that we are able to predict accurately
the quality above 50% of the time. This is still higher than random chance
at 16.6%, as there are 6 possible quality ratings to predict per wine.

We can observe that the highest gain in accuracy is obtained by adding the
variables alcohol (model m2) and sulphates (model m5) to the model. The highest
accuracy is achieved by including all variables in the model (model m7) with
a score of 0.58.

This score can be almost achieved with only 2 variables of the model m2 with
volatile acidity and alcohol.

The limitations of this exercise are:

* the choice of the model: choosing multinomial logistics regression may not be
the best adapted model. We could explore further classification models like
Naive Bayes, Decision Trees, Support Vector Machines, Neural Networks.
* the absence of cross-validation: we have trained the model on one training
set.
We could further explore this area.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}
ggplot(data = wine, aes(x = quality, y = volatile.acidity)) +
  geom_boxplot() +
  scale_color_brewer(palette = 'RdYlGn') +
  ylim(c(0.2, 1.2)) +
  labs(colour = 'Quality', x = 'Quality', y ='Volatile acidity (g/L)') +
  labs(title = 'Volatile acidity distribution by quality rating')
```

### Description One

This plot shows the distribution of volatile acidity for each quality rating.
We can visualize with the position of the boxplots that the volatile acidity
tends to be lower for higher quality rated wines. Only wines rated 7 and 8 
have similar distributions for volatile acidity. This makes the volatile acidity
the best candidate for a primary predictor of red wine quality.

### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
ggplot(data = wine, aes(x = citric.acid, y = volatile.acidity,
                        color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  scale_color_brewer(palette = 'RdYlGn') +
  geom_smooth(method = lm, se = FALSE) +
  xlim(c(0, 0.8)) +
  ylim(c(0.2, 1.2)) +
  labs(colour = 'Quality', x = 'Citric acid (g/L)',
       y ='Volatile acidity (g/L)') +
  labs(
    title = 'Quality rating as a function of volatile acidity and citric acid')
```

### Description Two

This plot shows by quality rating, how the wines are distributed in terms of
volatile acidity and citric acid concentration.

We can observe that the green points (high quality wines with a rating of 7 or
8) tend to be clustered around high citric acid concentration (0.25 to 0.75 g/L)
and low volatile acidity (0.2 to 0.6 g/L). Low quality wines tend to be
clustered around low citric acid concentration (below 0.25 g/L) and high
volatile acidity (above 0.6).

This clustering indicate that the combination of volatile acidity and citric
acid concentration would make good predictors for wine quality.

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
ggplot(data = wine, aes(x = alcohol, y = volatile.acidity, color = quality)) +
  geom_jitter(alpha = 0.75, size = 2) +
  scale_color_brewer(palette = 'RdYlGn') +
  geom_smooth(method = lm, se = FALSE) +
  xlim(c(8, 14)) +
  ylim(c(0.2, 1.2)) +
  labs(colour = 'Quality', x = 'Alcohol (%)', y ='Volatile acidity (g/L)') +
  labs(title = 'Quality rating as a function of alcohol and volatile acidity')
```

### Description Three

This plot shows by quality rating, how the wines are distributed in terms of
volatile acidity and alcohol content.

We can observe that the green points (high quality wines with a rating of 7 or
8) tend to be clustered around high alcohol content (10 % and above)
and low volatile acidity (0.2 to 0.6 g/L). Low quality wines tend to be
clusteredaround low alcohol content (below 10 %) and high volatile acidity
(above 0.6).

This clustering indicate that the combination of volatile acidity and alcohol
content would make good predictors for wine quality.
------

# Reflection

In this analysis, there were around 1,600 observations with 11 variables to
consider. We have started by plotting univariate plots to understand
the data structure. Then we looked at relationships between the label of
of study (quality) against other features. We isolated the pairs that displayed
the strongest relationship on a pair plot. We explored further by plotting
bi-variate plots and ultimately multi-variate plots. We eventually started a
quick prediction model based on an ordinal logistics regression.

The analysis revealed that volatile acidity and alcohol contents were good
predictors of the wine quality. The volatile acidity tends to be lower for
higher quality rated wines (below 0.6 g/L) . This is to be expected as high
volatile acidity is largely comprised of acetic acid (vinegar), which is 
associated with unpleasant taste.

The analysis confirms the influence of alcohol content in the wine quality. This
is to be expected as tasters would expect from a red wine a stronger body.

The influence of fixed acidity was not clearly demonstrated by the model (m4).
This is not surprising, as citric acid - a desired acid for its softer acid
taste and pleasant aromatic properties - is only one of its many constituents.

It was surprising to see that chlorides and sulfur dioxides did not appear
to be good predictors. Naturally, one would think that those chemical
properties, associated with negative perception (taste or health), would be good
indicators of lower wine quality.

Overall, acceptable prediction of the wine quality can already be achieved
with only 2 variables of the model m2 with volatile acidity and alcohol.

There are several axes of further exploration and improvement in the prediction
by deep-diving:

* the influence of other chemical properties: glycerol (a contributor for the
mouth-feel and texture), amino acids, tannin, minerals etc.
* the choice of the machine learning model to apply : choosing multinomial
logistics regression may not be the best adapted model. We could explore further
classification models like Naive Bayes, Decision Trees, Support Vector Machines,
Neural Networks etc.
* the fine-tuning of the model hyperparameters: no adjustment at all was done 
in this exercise.
* the machine learning model cross-validation: we have trained the model on
one training set. We could further explore this area.

#### Reference
* http://waterhouse.ucdavis.edu/whats-in-wine/
* https://www.r-bloggers.com/how-to-perform-a-logistic-regression-in-r/
* https://stat.ethz.ch/pipermail/r-help/2003-May/033335.html
* https://stats.idre.ucla.edu/r/dae/ordinal-logistic-regression/
* ggplot, ggally and R documentation
